Model and priors

### 2020-07-14 Code/Rmd/model.Rmd
Avoid uniform priors for distributional parameters for faster and more reliable convergence.

$$
\begin{aligned}proportion_{ij} \sim \frac{asym}{1 + e^{(mid_i-age) \times steep}} \\ asym \sim Normal(0.79, 0.1) \\ steep \sim Normal(1.76, 0.8) \\ mid \sim Beta(\mu_i, \phi) \\ \mu_i = \beta_0 + TE_{0i} + \beta_1 \times dominance_i + \beta_2 \times cognateness_i \\ \beta_0 \sim Normal(4.50, 1) \\ \beta_1 \sim Normal(0, 10) \\ \beta_2 \sim Normal(0, 10) \\ \phi \sim Normal(1.5, 1)
\end{aligned}
$$

>>>>

$$
\begin{aligned}proportion_{ij} \sim \frac{asym}{1 + e^{(mid_i-age) \times steep}} \\ asym \sim Normal(0.79, 0.1) \\ steep \sim Normal(1.76, 0.8) \\ mid \sim Beta(\mu_i, \phi) \\ \mu_i = \beta_0 + TE_{0i} + \beta_1 \times dominance_i + \beta_2 \times cognateness_i \\ \beta_0 \sim Normal(4.50, 1) \\ TE_{0i} \sim Normal(0, \sigma_i) \\\beta_1 \sim Normal(0, 10) \\ \beta_2 \sim Normal(0, 10) \\ \phi \sim Normal(1.5, 1)\\ \sigma_i \sim HalfCauchy(5)
\end{aligned}
$$
